### 2022-03-05 paper/fse22/approach.tex
approach

\Model generates input \sents with the following phases illustrated
in \ref{fig:OverallModel}: 1. search phase searches seed \sents
according to its \req of \lc, 2. seed parsing phase parses the
found seed \sents and extract their \cfg, 3. reference phase
collects large corpus, 4. syntax expansion identification, and
5.\sent expansion and generation. In this section, we provide more
details on each phase.

@@

>>>>

\Model generates input \sents with the following phases illustrated in
\ref{fig:OverallModel}: 1. search phase searches seed \sents according
to its \req of \lc, 2. seed parsing phase parses the found seed \sents
and extract their \cfg, 3. reference phase collects large corpus,
4. syntax expansion phase identifies structure for input augmentation,
and 5.\sent expansion phase generates natural expanded \sent. In this
section, we provide more details on each phase.

@@

\subsection{Seed parsing phase}
In the seed parsing phase,

\subsection{Reference phase}

\subsection{Syntax expansionphase}

\subsection{\Sent expansion phase}
